%*******************************************************
% Acknowledgments
%*******************************************************

\pdfbookmark[1]{Acknowledgments}{acknowledgments}

%\begin{flushright}{\slshape    
%    Let the machine take care of the machines, \\
%    and I'll go spend more time with my family, \\
%    or golf.} \\ \medskip
%    --- Mark Goddard
%\end{flushright}
%
%\begin{flushright}{\slshape    
%    Statistics is the art of never having to say you’re wrong. \\ Variance is what any two statisticians are at.} \\ \medskip
%    --- C. J. Bradfield
%\end{flushright}

\begin{flushright}{\slshape    
    To me, mathematics, computer science and the arts are insanely related. They're all creative expressions.} \\ \medskip
    --- Sebastian Thrun
\end{flushright}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgments}

I would like to thank Professor Peter Glösekötter, who has been supportive since the days I was an undergraduate student, and whose drive for innovation I admire. It was with his supervision that this work came into existence. In addition to my stay in Brazil, he enabled me to both work and pursue my studies in England, Spain, and China. Thank you for the excellent cooperation and for all of the opportunities I was given to, besides boosting my technical skills, broaden my personal horizons during this incredibly instructive period.

Also, I must express my sincere gratitude to Mariana Kolberg and Edson Prestes for co-supervising this work. Thank you for the lively discussions and your patient mentoring. Collaborating with you and the whole team of the $\Phi$-Robotics Research Group has enriched my experience in Porto Alegre tremendously. I have been extremely lucky to have been surrounded by people like you, who cared so much about my work and who responded to my questions and queries so promptly. 

%I am gratefully indebted to your very valuable comments on this thesis.

My wholehearted gratefulness and appreciation goes to Mathias Mantelli, who helped me grow personally beyond my work at the keyboard and who cheered me up during the most difficult times when writing this thesis. Without him, I would have been lost many times. Our stimulating discussions and his attention to detail profoundly contributed in the completion of this thesis. Thank you for all the fun we had in the past six months.

I heartily dedicate this thesis to my mother Karin and to my brother Manuel, whose love and guidance are with me in whatever I pursue. Thank you for providing me with unfailing support and continuous encouragement throughout my years of study and through the process of researching and writing this thesis. What I have accomplished would not have been possible without you.

Last but not least, I would like to express my very profound gratitude to my friends Nina, Denise, Sebastian and Tim. I am so blessed to have you by my side. During all the months-long periods that I spent abroad, you were the ones who waited patiently for me to return whilst encouraging me from back home.

\bigskip
\noindent
Thank you all for your unwavering support.

\bigskip
\noindent
Rob

\endgroup



